Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-07-10 paper.tex
nice

Many types of post-translational modification (PTM) are known, and databases containing detailed information about such modifications are readily available\cite{Creasy_2004}.
Information about a modification often includes the chemical or isotopic composition, mass, specificity to certain residues, and possible restriction of placement to peptide or protein termini.
Protein databases such as UniProt include information on the localization of specific modifications to specific residues in the protein, but this information is incomplete.
Despite the extensive cataloging of the different possible protein modifications, their comprehensive discovery and identification in complex biological samples has continued to pose a challenge for proteomics\cite{Olsen_2013}.

Numerous procedures for identification and localization of PTMs from "bottom-up" tandem mass spectrometric datasets exist, and those mostly concentrate on common modifications (e.g. phosphorylations) in well-studied systems.
Global discovery tools, such as MODa\cite{Na_2011} are also available.
G-PTM-D\cite{Li_2016}, is one recently described bioinformatics tool for high confidence identification and localization of a wide variety of different PTMs at the same time.
The G-PTM-D workflow consists of three stages: 1) A wide-mass database search\cite{Chick_2015, Na_2011}, that provides mass differences between the identified peptides and the measured parent peptide masses (hypothesized to differ in mass due to the presence of a PTM)
2) For those peptides for which the mass difference corresponds to the mass of a known PTM, a database augmentation step adds plausible localized PTMs to the proteins in the search database
3) A final standard narrow-mass search of the augmented database to identify both modified and unmodified peptides subject to the standard FDR threshold (e.g. 1\% FDR).

>>>>

Many types of post-translational modifications (PTMs) are known, and databases containing detailed information about such modifications are readily available\cite{Creasy_2004}.
Information about a modification often includes the chemical or isotopic composition, mass, specificity to certain residues, and possible restriction of placement to peptide or protein termini.
Protein databases such as UniProt include information on the localization of specific modifications to specific residues in the protein, but this information is incomplete.
Despite the extensive cataloging of the different possible protein modifications, their comprehensive discovery and identification in complex biological samples has continued to pose a challenge for proteomics\cite{Olsen_2013}.

Numerous procedures for identification and localization of PTMs from "bottom-up" tandem mass spectrometric datasets exist, and those address primarily common modifications (e.g. phosphorylations) in well-studied systems.
Global discovery tools, such as MODa\cite{Na_2011} are also available.
G-PTM-D\cite{Li_2016} is one recently described bioinformatics tool for high confidence identification and localization of a wide variety of different PTMs.
The G-PTM-D workflow consists of three stages: 1) A wide-mass database search\cite{Chick_2015, Na_2011}, that provides mass differences between the identified peptides and the observed precursor peptide masses (hypothesized to differ in mass due to the presence of a PTM);
2) For those peptides for which the mass difference corresponds to the mass of a known PTM, a database augmentation step adds plausible localized PTMs to the corresponding protein entries in the search database;
3) A final standard narrow-mass search of the augmented database to identify both modified and unmodified peptides subject to the standard FDR threshold (e.g. 1\% FDR).
